%-------------------------
% Resume in Latex
% Adapted for Truong Nguyen Minh Hieu
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.9in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Truong Nguyen Minh Hieu} \\
    \vspace{8pt}
    \small
    \faIcon{github}
    \href{https://github.com/HieuThu16}{\underline{github.com/HieuThu16}} \quad
    \faIcon{code}
    \href{https://hieuthu16.github.io/HieuThu16/}{\underline{Portfolio}} \quad
    \faIcon{envelope}
    \href{mailto:truongnguyenminhhieu100@gmail.com}{\underline{truongnguyenminhhieu100@gmail.com}}
\end{center}

\section{Summary}
\small{Full-stack developer building practical web products with React, Next.js, Java, and Spring Boot. My work focuses on fast interfaces, clear structure, and small systems that are easy to ship, maintain, and improve.}

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: React, Next.js, TypeScript, JavaScript, Tailwind CSS, Progressive Web Apps} \\
     \textbf{Backend}{: Java, Spring Boot, REST APIs} \\
     \textbf{Tools}{: Git, GitHub Actions, Vercel, VS Code} \\
     \textbf{Other}{: C\#, content-heavy UI design, responsive layouts}
    }}
 \end{itemize}

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{phimfree} $|$ \footnotesize\emph{Next.js, React, TypeScript, Tailwind CSS, Vercel}}{Live Project}
    \resumeItemListStart
      \resumeItem{Built a movie streaming and discovery interface with category, country, and catalog browsing.}
      \resumeItem{Focused on dense content layouts, quick navigation, and a lightweight public deployment flow.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{ReadBook PWA} $|$ \footnotesize\emph{React, JavaScript, PWA, Vercel}}{Live Project}
    \resumeItemListStart
      \resumeItem{Built an installable reading library with category-driven browsing and a mobile-friendly layout.}
      \resumeItem{Structured the app to keep the reading flow lightweight and usable across devices.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Learn\_Spring-Boot} $|$ \footnotesize\emph{Java, Spring Boot, GitHub}}{Practice Project}
    \resumeItemListStart
      \resumeItem{Used hands-on exercises to learn backend structure, service layers, and API-oriented application flow.}
      \resumeItem{Supported the shift from frontend-first work into broader full-stack development.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Independent Product Development}{2024 -- Present}
    {Personal projects, portfolio work, and continuous learning}{Vietnam}
    \resumeItemListStart
      \resumeItem{Built and deployed personal web products with React, Next.js, TypeScript, and Vercel-based workflows.}
      \resumeItem{Explored backend structure and API design through Java and Spring Boot practice repositories and course projects.}
      \resumeItem{Maintained a public GitHub profile with demos, study repositories, and iterative learning across JavaScript, Java, C\#, and algorithms.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}